Homework_2_Submission

### 2022-09-05 hw2/ashish/a.0_kfold_knnn.Rmd

```{r, include = FALSE}
#Iterate over k and get mean test
acc_df <- data.frame(matrix(ncol = 0, nrow = length(seq(3,25,2))))
acc_df$k_kknn = seq(3,25,2)
mean_cv_acc_k = lapply(seq(3,25,2), function(x) mean(unlist(cv_function(df = df_copy,x))))
min_cv_acc_k = lapply(seq(3,25,2), function(x) min(unlist(cv_function(df = df_copy,x))))
acc_df$mean_cv_accuracy = unlist(mean_cv_acc_k)
acc_df$min_cv_accuracy = unlist(min_cv_acc_k)
#mean(unlist(cv_accuracy))
```

@@

>>>>

```{r, include = FALSE}
#Iterate over k and get mean test
acc_df <- data.frame(matrix(ncol = 0, nrow = length(seq(3,101,2))))
acc_df$k_kknn = seq(3,101,2)
mean_cv_acc_k = lapply(seq(3,101,2), function(x) mean(unlist(cv_function(df = df_copy,x))))
min_cv_acc_k = lapply(seq(3,101,2), function(x) min(unlist(cv_function(df = df_copy,x))))
acc_df$mean_cv_accuracy = unlist(mean_cv_acc_k)
acc_df$min_cv_accuracy = unlist(min_cv_acc_k)
#mean(unlist(cv_accuracy))
```

@@

```{r}
ggplot(data = acc_df, aes(x = k_kknn, y = mean_cv_accuracy)) +
  geom_line() +geom_point() +
  geom_vline(xintercept = acc_df[which.max(acc_df$mean_cv_accuracy),1],
             color ="magenta", size = 1.5, alpha = 0.5)
```

### 2022-09-05 hw2/submission.Rmd

---
title: "Homework_2"
output: html_document
date: "2022-09-04"
---

@@

## Question 3.1

```{r}
cc_data = read.table('./data 3.1/credit_card_data-headers.txt', header = TRUE, sep='', dec='.')
head(cc_data)
dim(cc_data)
```

## Question 4.2

```{r}
iris_data = read.table('./iris.txt', header = TRUE, sep='', dec='.')
head(iris_data)
dim(iris_data)
```

### Exploratory Data Analysis

```{r}
summary(iris_data)
```

```{r}
table(iris_data$Species)
```

```{r}
# Density Plots
my_plots = lapply(colnames(iris_data), function(x){
  p = ggplot(iris_data) + aes_string(x)
  if(x=='Species') {
    p = p + geom_bar()
  }
  else {
    p = p + geom_density()
  }
})

plot_grid(plotlist = my_plots)
```

```{r}
# Correlation Matrix
cor_mat = round(cor(iris_data[,1:4]), 2)
melted_mat = melt(cor_mat)
ggplot(melted_mat, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() + geom_text(aes(Var1, Var2, label=value), color='white', size=3)
```

### Modelling

```{r}
# Calculation of best 'K'
elbow_graph_data <- data.frame(K=integer(), sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  elbow_graph_data[nrow(elbow_graph_data) + 1, ] = c(k, km.res$tot.withinss)
}
```

```{r}
elbow_graph_data
```

```{r}
plot(elbow_graph_data, type='b', ylab='Total Sum of Square Within', main='Elbow Graph', )
```

Best K is 3 because we are getting marginal benefit after that

```{r}
best_km <- kmeans(as.matrix(scale(iris_data[,1:4])), 3, nstart = 25)
best_km
```

```{r}
cm <- table(iris_data$Species, best_km$cluster)
cm
```

```{r}
best_km$centers
```

```{r}
# renaming predicted clusters according to categorical response variable
# renamed_clusters <- c("versicolor", "setosa", "virginica")[best_km$cluster]
```

```{r}
kmeans_basic_table <- data.frame(best_km$size, best_km$centers)
kmeans_basic_table
```

```{r}
kmeans_basic_df <- data.frame(actual_value=iris_data[,5], prediction=best_km$cluster)
kmeans_basic_df
```

```{r}
plot(scale(iris_data[,1:4]), col=best_km$cluster)
```

```{r}
# prediction_accuracy <- round(sum(kmeans_basic_df$actual_value == kmeans_basic_df$prediction) / nrow(kmeans_basic_df) * 100, 2)
# print(paste('Accuracy Acheived ->', prediction_accuracy, '%' ))
```

### Plotting Clusters

```{r}
fviz_cluster(best_km, data=scale(iris_data[,1:2]), geom=c("point"), ellipse.type = "euclid")
```
***Analysing For K=4***

```{r}
alt_kmeans <- kmeans(as.matrix(scale(iris_data[,1:4])), 4, nstart = 25)
alt_kmeans
```

```{r}
cm <- table(iris_data$Species, alt_kmeans$cluster)
cm
```

```{r}
alt_kmeans$centers
```

```{r}
alt_kmeans_table_size_v_centers <- data.frame(alt_kmeans$size, alt_kmeans$centers)
alt_kmeans_table_size_v_centers
```

```{r}
alt_kmeans_row_pred <- data.frame(actual_value=iris_data[,5], prediction=alt_kmeans$cluster)
alt_kmeans_row_pred
```

```{r}
# clusters = data.frame(alt_kmeans$cluster)
# clusters[clusters$alt_kmeans.cluster==4,]
mapped_data <- data.frame(iris_data[,1:4], prediction=alt_kmeans$cluster)
```

```{r}
# Summary for Cluster 1
summary(mapped_data[mapped_data$prediction==1,1:4])
```

```{r}
# Summary for Cluster 2
summary(mapped_data[mapped_data$prediction==2,1:4])
```

```{r}
# Summary for Cluster 3
summary(mapped_data[mapped_data$prediction==3,1:4])
```

```{r}
# Summary for Cluster 4
summary(mapped_data[mapped_data$prediction==4,1:4])
```

```{r}
plot(scale(iris_data[,1:4]), col=best_km$cluster)
```

```{r}
fviz_cluster(best_km, data=scale(iris_data[,1:2]), geom=c("point"), ellipse.type = "euclid")
```

>>>>

---
title: "Homework_2_Submission"
output: html_document
date: "2022-09-04"
---

@@
